---
title: "Weight of Fish"
author: "Cyann Arevalo"
date: "Fall 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
require(car)
```

```{r}
fishD = read.csv("Fish.csv")
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

 In order to predict weight, we will use numerical~numerical due to the variables we are looking at, since they are all numerical explanatory variables.
 
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
FishiesP=filter(fishD, Species=="Perch")
FishiesP= select(FishiesP, -Species)
pairs(FishiesP)
```


```{r}
FishiesB=filter(fishD, Species=="Bream")
FishiesB= select(FishiesB, -Species)
pairs(FishiesB)
```


```{r}
FishiesS=filter(fishD, Species=="Smelt")
FishiesS= select(FishiesS, -Species)
pairs(FishiesS)
```


<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->





### Numerical Descriptive Results

```{r}
summary(FishiesP)
summary(FishiesB)
summary(FishiesS)
```


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
fishPerch=lm(Weight~Length2+Width,data=FishiesP)
summary(fishPerch)
```

  According to the summary above, we can see that the Adjusted R-Squared is 0.9645.



```{r}
fishBream=lm(Weight~Length2+Width,data=FishiesB)
summary(fishBream)
```
  
  For Bream, we can see an Adjusted R-Squared of 0.9116.

```{r}
fishSmelt=lm(Weight~Length2+Width,data=FishiesS)
summary(fishSmelt)
```
When looking at the numerical summary for Smelt, we can see an Adjusted R-Squared of 0.9465.


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesP,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

  By looking at the model above, we can see that the best two explanatory variables are Height and Width at an Adjusted R-Squared of about 0.94, which is very close to the Ajusted R-Squared of 0.9645 that we saw above. 



```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesB,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

  When it comes to Bream according to the model above, the best two explanatory variables for determining weight are Length2 and Height with an Adjusted R-Squared of about 0.936. 


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = FishiesS,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
  When looking at the model for Smelt, we can see that the best two explanatory variables for determining weight are Length2 and Width whose Adjusted R-Squared is around 0.96. This is very close to the 0.9465 we saw earlier in the numerical summary.
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

   We used three models to predict the weight of these fish.
   
   For Perch, we could see that the best two explanatory variables we can use to determine weight are Height and Width.
   
   
   For Bream, the best two explanatory variables for determining weight are Length2 and Height.
   
   
   For Smelt, the best two explanatory variables we could use to determine weight are Length2 and Width.
   